Modelling the emergence of whisker barrels

### 2020-06-19 paper/briefpaper/brief.tex
more resolved conflicts

The only differences between thalamic projections are their strengths of
interaction with the guidance fields, $\gamma$, hence any reliable differences
between emergent cortical fields must be due to differences in these values
only. We speculate that the contribution of a given ephrin field, to the
velocity at which a projection migrates across the cortical subplate, is
determined by the concentration of a similar molecule at its thalamic origin,\stu{We concentrate on the representation of the 41 macrovibrissae because their thalamic and cortical correlates are easily identifiable and consistently positioned, we exclude the microvibrissae to limit the complexity of the simulations, and we exclude the five rhinal whiskers as their representation in S1 is isolated from the main barrel field.} A cortical boundary enclosing \stu{the} 41 \cmnt{macrovibrissae} barrels was traced from
a cytochrome oxidase stain from \cite{zheng_signal_2001} \cmnt{(using the
  authors' original data)}, and Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved
for $N=41$ projections on the resulting domain, using $M=2$ linear signalling
gradients aligned with the anterior-posterior and medial-lateral axes.

i.e., the putative barreloid center. \stu{As such, we consider linear gradients aligned to anterior-posterior and medial-lateral axes through the VPM, and as $\gamma$-values use the coordinates of the barreloid centers in these axes as they appear in \citep{haidarliu_size_2001} (Fig.\,\ref{fig:main}B).} \stu{Complementary thalamic and cortical molecular guidance gradients of this form have been well established experimentally} \citep{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}, \stu{e.g., cells originating in the medial part of ventrobasal thalamus (comprising VPM and VPL) express high levels of EphA receptors and project to the lateral part of S1, which expresses low levels of ephrin-A5, and cells originating in the lateral part of ventrobasal thalamus express low levels of EphA receptors and project to the medial part of S1, which expresses high levels of ephrin-A5 (see} \citealp{gao_regulation_1998,dufour_area_2003,vanderhaeghen_developmental_2004,speer_grading_2005}). \stu{We concentrate on the representation of the 41 macrovibrissae because their thalamic and cortical correlates are easily identifiable and consistently positioned, we exclude the microvibrissae to limit the complexity of the simulations, and we exclude the five rhinal whiskers as their representation in S1 is isolated from the main barrel field.} A cortical boundary enclosing \stu{the} 41 \cmnt{macrovibrissae} barrels was traced from
a cytochrome oxidase stain from \cite{zheng_signal_2001} \cmnt{(using the
  authors' original data)}, and Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved
for $N=41$ projections on the resulting domain, using $M=2$ linear signalling
gradients aligned with the anterior-posterior and medial-lateral axes.

>>>>

The only differences between thalamic projections are their strengths of
interaction with the guidance fields, $\gamma$, hence any reliable differences
between emergent cortical fields must be due to differences in these values
only. We speculate that the contribution of a given ephrin field, to the
velocity at which a projection migrates across the cortical subplate, is
determined by the concentration of a similar molecule at its thalamic origin, i.e., the putative barreloid center.

\stu{As such, we consider linear gradients aligned to anterior-posterior and medial-lateral axes through the VPM, and as $\gamma$-values use the coordinates of the barreloid centers in these axes as they appear in \citep{haidarliu_size_2001} (Fig.\,\ref{fig:main}B).} \stu{Complementary thalamic and cortical molecular guidance gradients of this form have been well established experimentally} \citep{vanderhaeghen_mapping_2000,miller_epha7-ephrin-a5_2006}, \stu{e.g., cells originating in the medial part of ventrobasal thalamus (comprising VPM and VPL) express high levels of EphA receptors and project to the lateral part of S1, which expresses low levels of ephrin-A5, and cells originating in the lateral part of ventrobasal thalamus express low levels of EphA receptors and project to the medial part of S1, which expresses high levels of ephrin-A5 (see} \citealp{gao_regulation_1998,dufour_area_2003,vanderhaeghen_developmental_2004,speer_grading_2005}). \stu{We concentrate on the representation of the 41 macrovibrissae because their thalamic and cortical correlates are easily identifiable and consistently positioned, we exclude the microvibrissae to limit the complexity of the simulations, and we exclude the five rhinal whiskers as their representation in S1 is isolated from the main barrel field.}

A cortical boundary enclosing \stu{the} 41 \cmnt{macrovibrissae} barrels was traced from
a cytochrome oxidase stain from \cite{zheng_signal_2001} \cmnt{(using original data kindly supplied by the authors)}, and Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved for $N=41$ projections on the resulting domain, using $M=2$ linear signalling gradients aligned with the anterior-posterior and medial-lateral axes.
